Spin canonical divisors of log stacky curves

### 2015-06-30 stacky_write_up/spin_cring.tex
beamer skeleton, correct kodaira-spencer bib entry

\todo{Peter: I think we need something about odd weight modular forms before going right into stacks.}  
Following Voight and Zureick-Brown \cite{vzb:stacky}, we generalize Petri's theorem in many \todo{Peter: not clear to me that ``many'' is a good word to use here.  We mostly generalize in one direction}
directions. 
If $X$ is a curve, \todo{why do you start with a curve and then move to a stacky curve? shouldn't it be the opposite order?} then we say $\sx$ is a {\bf stacky curve} with {\bf coarse space} $X$ and {\bf stacky points} (also called {\bf{fractional points}}) $P_1,\ldots, P_r$ with {\bf stabilizer orders} $e_1,\ldots, e_r \in \BZ_{\geq 2}$ if 
\[
\di \sx = \di X \oplus \left(\bigoplus_{i
= 1}^r \left\langle \frac{1}{e_i}P_i \right\rangle \right) \subset \BQ \otimes \di X.
\]
\todo{Peter: Would it be better to say $Div(\sx)=(Div(X))[\frac{1}{e_i}P_i]_{1\le i\le r}$ or something like that?}
As is done in Voight and Zureick-Brown \cite{vzb:stacky} stacky curves may be formalized as stacks, but for the purposes of this paper, it suffices to view $\sx$ as a scheme whose associated divisor group allows a finite number of stacky points. \todo{I don't know if this is a good statement to make.  We aren't really viewing $\sx$ as a scheme.  Rather we're are determining information about its canonical rings through knowledge of scheme data.}  A {\bf log spin curve} is a triple $(\sx, \Delta, \halfcan)$ where $\Delta \in \di X$ is an effective divisor and $2\halfcan = K_X + \Delta + \sum_{i=1}^{r}\subhalf{e_i}P_i.$
The central object of study in this paper is the {\bf log spin
canonical ring} of $(\sx, \Delta, \halfcan)$ is
\begin{align*}
	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(\sx,\lfloor d \halfcan \rfloor)
\end{align*}

@@

\todo{do this part}
Part on Kodaira--Spencer \cite{kodaira:complex-manifolds}.

>>>>

\todo{Peter: I think we need something about odd weight modular 
forms before going right into stacks.}
Following Voight and Zureick-Brown \cite{vzb:stacky}, we generalize 
Petri's theorem in many \todo{Peter: not clear to me that ``many'' 
is a good word to use here.  We mostly generalize in one direction}
directions.

If $X$ is a curve, \todo{why do you start with a curve and then
move to a stacky curve? shouldn't it be the opposite order?} then
we say $\sx$ is a {\bf stacky curve} with {\bf coarse space} $X$
and {\bf stacky points} (also called {\bf{fractional points}}) $P_1,
\ldots, P_r$ with {\bf stabilizer orders} $e_1,\ldots, e_r \in \BZ_{
\geq 2}$ if 
\[
	\di \sx = \di X \oplus \left(\bigoplus_{i = 1}^r \left\langle 
	\frac{1}{e_i}P_i \right\rangle \right) \subset \BQ \otimes \di X.
\]
\todo{Peter: Would it be better to say $Div(\sx)=(Div(X))[\frac{1}{e_i}P_i]_{1\le i\le r}$ or something like that?}
As is done in Voight and Zureick-Brown \cite{vzb:stacky} stacky curves may be formalized as stacks, but for the purposes of this paper, it suffices to view $\sx$ as a scheme whose associated divisor group allows a finite number of stacky points. \todo{I don't know if this is a good statement to make.  We aren't really viewing $\sx$ as a scheme.  Rather we're are determining information about its canonical rings through knowledge of scheme data.}  A {\bf log spin curve} is a triple $(\sx, \Delta, \halfcan)$ where $\Delta \in \di X$ is an effective divisor and $2\halfcan = K_X + \Delta + \sum_{i=1}^{r}\subhalf{e_i}P_i.$
The central object of study in this paper is the {\bf log spin
canonical ring} of $(\sx, \Delta, \halfcan)$ is
\begin{align*}
	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(\sx,\lfloor d \halfcan \rfloor)
\end{align*}

@@

\todo{do this part}
Part on Kodaira--Spencer \cite{kodaira-spencer:deformations}.
